% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Adam S. Bradfield}
\address{Brooklyn, NY \linebreak github.com/adam7397}
\contacts{linkedin.com/in/adambfd/ \linebreak adamsbradfield@gmail.com}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
        \begin{cvsubsection}{Software Development Eng. II, Android}{Audible, Inc.}{January 2024 -- Present}
		\vspace{2mm}
			\begin{itemize}
				\item Lead development of new discovery experience
				\item Currently helping re-write Kindle application using C++
				\item Modularized code throughout the app to improve efficiency
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Software Development Eng. II, Credit Systems}{Audible, Inc.}{April 2023 -- December 2023}
		\vspace{2mm}
			\begin{itemize}
				\item Lead API migration from shared service to team owned service
				\item Facilitated architecture reviews, deployments, and end-to-end testing
				\item Certified one of the team's primary software packages to internal security standards
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Development Engineer, Android}{Audible, Inc.}{March 2021 -- March 2023}
		\vspace{2mm}
			\begin{itemize}
				\item Lead two large features bringing 'Series' to Android
				\item Coordinated new app version releases, created automatic publishing of our builds to Google Play
				\item Rewrote user library logic to make use of Kotlin Coroutines
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Web Experience Engineer, Identity Cloud}{Akamai Technologies}{May 2019 -- March 2021}
		\vspace{2mm}
			\begin{itemize}
				%\item Employed background of Web Apps and System Design to assist with customer issues.
				\item Wielded Javascript \& Ruby tools to help debug highly customized implementations.
				\item Utilized APIs \& AWS to help provide consistent, working solutions.
			\end{itemize}
		\end{cvsubsection}
		
		% \begin{cvsubsection}{Web Experience Engineer, Co-Op}{Akamai Technologies}{January 2018 -- December 2018}
		% \vspace{2mm}
			% \begin{itemize}
				% \item Two separate co-ops focused on developing depth on Internet structure and the role of a CDN.
				% \item Developed a python script to help track delivery of content on Akamai enabled sites.
			% \end{itemize}
		% \end{cvsubsection}
		
		%\begin{cvsubsection}{Combat Systems Technology, Pathways Intern}{Naval Undersea Warfare Center}{June 2017 -- August 2017}
		%\vspace{2mm}
		%	\begin{itemize}
		%		\item Developed testing suite to help streamline server \& software integration.
		%		\item Project earned clearance for use on deployed submarine fleet.
		%	\end{itemize}
		%\end{cvsubsection}
		
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Cambridge, MA}{Harvard University}{June 2019 -- May 2024}
		
			\begin{itemize}
				\item A.L.M in Extension Studies, Software Engineering. GPA: 3.7
				\item Coursework: Data Structures \& Algorithm, Systems Programming \& Machine Org.; Theoretical Comp. Sci.; Discrete Math; Software Design; Cloud Computing; Deep Learning for NLP; Bayesian Inference
				\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Boston, MA}{Wentworth Institute of Technology}{September 2015 -- April 2019}
		\vspace{2mm}
			\begin{itemize}
				\item B.S. in Computer Science. GPA: 3.5
				\item Coursework: Operating Systems; Databases; Data Structures; Algorithms; Programming Languages; Parallel Computing; Data Science; Software Engineering; Linear Algebra \& Matrix Theory
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
                \item \textbf{Publications Office of the European Union}: Created a web application \& backend to leverage LLM to summarize EU Legislation \& was deployed on AWS. Python; JavaScript; CSS.
				\item \textbf{Shell}: Developed a command line shell with support for variable substitution, piping, redirects, conditionals, and background commands. C++.
				\item \textbf{WeensyOS}: Implemented process memory isolation, virtual memory, and system calls into a basic operating system. C++.
				% \item \textbf{Conference Coordinator}: Worked in a team of 13 to put together a web-app based on monitoring attendance \& engagement at a coding conference. Go; HTML; Typescript; Docker.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Java; Kotlin; Pytthon; C++; Golang; C
				\item AWS; Git; Android Studio
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	%\begin{cvsection}{Additional Experience and Awards}
	%	\begin{cvsubsection}{}{}{}	
	%		\begin{itemize}
	%			\item \textbf{Eagle Scout (2013):} Achieved the rank of Eagle with my troop in RI.
	%			\item \textbf{Resident Assistant (2016 -- 2019):} Created fun and safe environments for students to learn, connect, \& thrive.
	%		\end{itemize}
	%	\end{cvsubsection}
	%\end{cvsection}
		
\end{document}
